\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}	

\usepackage{amsmath,amsthm,amssymb,amscd}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\newlength{\tabcont}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
\parindent 0in
\parskip 12pt
\geometry{margin=1in, headsep=0.25in}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{reg}{Rule}
\newtheorem{exer}{Exercise}
\newtheorem{note}{Note}

\begin{document}

\title{Introduction to WSS '17 - Lecture 1, 9am-10am}

\thispagestyle{empty}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\LARGE \bf Morning Session: GitHub, The Art of Project Development, Notebook Documents, 9am-12am}\\
\medskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large \today}\\
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   COURSE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\large Wolfram Summer School 2017}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   ANNOUNCEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   AGENDA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Agenda}
\begin{enumerate}
\item GitHub account and repo creation
\item The Art of Project Development
\item Notebook Documents
\end{enumerate}

\noindent\hrulefill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   RECAP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   TODAY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{GitHub}

Created a repo and gave Giulio write permissions. Cloned the starthere repo.

\section{The Art of Project Development}

\subsection{What NOT to do}

\begin{enumerate}
\item ``Infix gore": Don't be insanely verbose with infices.
\item ``Anonymous function galore": Name your variables when nesting functions! Not doing so makes for confusing code. 
\item Inconsistency - e.g., using different conventions within one definition
\item Naming functions in different languages...
\end{enumerate}

\subsection{What to do}

\begin{enumerate}
\item Use code cells! This can be done with command+8.
\item Indent! In particular, if the expression doesn't fit in a single line, indent using multiple lines.
\item Use whitespace around operators.
\item Never use infices in multiline code.
\item It's good to adopt the convention of \verb|camelCasing| variable names, the way WL does.
\end{enumerate}

\subsection{TIPS}

\begin{enumerate}
\item Double- and triple-clicking to do selection of code. This shows the scope of some function. 
\begin{itemize}
\item This is possible to do by keyboard shortcut.
\end{itemize}
\end{enumerate}

\section{Notebook Documents}




\end{document}